Introduction to Moltres: an Application for Simulation of Molten Salt Reactors

### 2017-05-10 Moltres.tex
adds image sent by alex via email on May 9, 2017.

\begin{table}[htpb]
  \begin{center}
    \begin{tabular}{l | r}
      Component & Mass Fraction\\\hline\hline
      Li-7 & .1090\\
      Li-6 & 5$\cdot$10$^{-6}$\\
      F-19 & .6680\\
      Be-9 & .0627\\
      U-235 & .0167\\
      U-238 & .0344\\
    \end{tabular}
  \end{center}
  \caption{Fuel salt composition based on enriched Uranium \gls{MSRE} design \cite{robertson_msre_1965}}
  \label{table:comp}
\end{table}

@@

\begin{figure}
  \centering
  \includegraphics{auto_diff_rho_group1.eps}
  \caption{Group 1 flux}
  \label{fig:group1}
\end{figure}

\begin{figure}
  \centering
  \includegraphics{auto_diff_rho_group2.eps}
  \caption{Group 2 flux}
  \label{fig:group2}
\end{figure}

The effect of the advecting fuel is seen in \Cref{fig:temp} where the temperature
rises steadily with increasing z-coordinate. As one might expect, the temperature
gradient is negative in the radial direction.

\begin{figure}
  \centering
  \includegraphics{auto_diff_rho_temp.eps}
  \caption{Temperature}
  \label{fig:temp}
\end{figure}

@@

% Fix me! Precursor concentrations have goofy scaling
\begin{figure}
  \centering
  \includegraphics{auto_diff_rho_pre1.eps}
  \caption{Longest lived precursor concentration}
  \label{fig:pre1}
\end{figure}

@@

% Fix me! Precursor concentrations have goofy scaling
\begin{figure}
  \centering
  \includegraphics{auto_diff_rho_pre6.eps}
  \caption{Shortest lived precursor concentration}
  \label{fig:pre6}
\end{figure}

>>>>

\begin{table}[htpb]
  \begin{center}
    \begin{tabular}{l | r}
      Component & Mass Fraction\\\hline\hline
      Li-7 & .1090\\
      Li-6 & 5$\cdot$10$^{-6}$\\
      F-19 & .6680\\
      Be-9 & .0627\\
      U-235 & .0167\\
      U-238 & .0344\\
    \end{tabular}
  \end{center}
        \caption{Fuel salt composition is based on the \gls{BOL} enriched 
        uranium composition in the \gls{MSRE} design 
        \cite{robertson_msre_1965}.}
  \label{table:comp}
\end{table}

@@

\begin{figure}
  \centering
  \includegraphics{auto_diff_rho_group1.eps}
        \caption{The group 1 flux in this 2-D cylindrical axisymmetric model 
        has the anticipated magnitude and canonical cosine shape ($r=1$ is center of core). }
  \label{fig:group1}
\end{figure}

\begin{figure}
  \centering
  \includegraphics{auto_diff_rho_group2.eps}
        \caption{The group 2 flux in this 2-D cylindrical axisymmetric model 
        has the anticipated magnitude and canonical cosine shape ($r=1$ is center of core). }
  \label{fig:group2}
\end{figure}

\begin{figure}
  \centering
  \includegraphics{radial_group_comparison.eps}
        \caption{The thermal and fast flux profiles are compared at the 
        core center in this 2-D cylindrical axisymmetric model ($r=1$ is center of core). }
\end{figure}

The effect of the advecting fuel is seen in \Cref{fig:temp} where the temperature
rises steadily with increasing z-coordinate. As is accordingly expected, the temperature
gradient is negative in the radial direction.

\begin{figure}
  \centering
  \includegraphics{auto_diff_rho_temp.eps}
        \caption{The reactor core temperature peaks near the reactor outlet 
        in this 2-D axisymmetric model ($r=1$ is center of core).}
  \label{fig:temp}
\end{figure}

@@

% Fix me! Precursor concentrations have goofy scaling
\begin{figure}
  \centering
  \includegraphics{auto_diff_rho_pre1.eps}
        \caption{The concentration of the group of longest lived precursors 
        ($\lambda = ?$) peaks near the reactor outlet
        in this 2-D axisymmetric model ($r=1$ is center of core).}
  \label{fig:pre1}
\end{figure}

@@

% Fix me! Precursor concentrations have goofy scaling
\begin{figure}
  \centering
  \includegraphics{auto_diff_rho_pre6.eps}
        \caption{The concentration of the group of shortest lived precursors 
        ($\lambda = ?$) peaks near the reactor center
        in this 2-D axisymmetric model ($r=1$ is center of core).}
  \label{fig:pre6}
\end{figure}
